Development of a Reinforcement Learning Enabled Cattle Tracker Prototype

### 2025-02-13 paper/main.tex
Reformatted ref and added Conclusion

\section{Conclusion}

>>>>

\section{Conclusion}
In this study, we developed a reinforcement learning-enabled cattle tracker prototype designed to optimize power consumption while ensuring efficient data transmission and collection. The device successfully leverages reinforcement learning to dynamically adjust its operation based on available energy, enhancing battery life and operational efficiency. By incorporating solar power and an intelligent decision-making framework, the prototype demonstrates a feasible approach to long-term, autonomous cattle tracking.
Future work will focus on improving the efficiency of the reinforcement learning model by integrating real-time adaptation to environmental changes. Additional experiments in diverse field conditions will provide further validation of the system's robustness. Further refinements to the hardware, such as low-power components and custom PCB design, will enhance reliability and longevity. Moreover, expanding the cloud-based digital twin functionality can improve remote monitoring and predictive analytics for herd management.
